Optimal forward modeling of gravitational fields using tesseroids with adaptive discretization

### 2014-08-25 manuscript.tex
Made glq fail fig horizontal

%\documentclass[extra,mreferee]{gji}
% Use the option below to make a nicely formatted manuscript
\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{graphicx}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height and the Gauss-Legendre Quadrature order
        (number of nodes in each dimension).
        The $g_{xy}$ component caused by a
        $7^\circ \times 7^\circ \times 20\ km$ tesseroid
        with $2.67\ g.cm^{-3}$ density
        and top at $z=0$
        was calculated on a regular grid
        at different heights and using different orders.
        The GLQ order used was the same for all three dimensions.
        a) At $400\ km$ height and order 2, the effect is similar to that
        presented by \citet{Asgharzadeh2007}. b) At $150\ km$ height and order
        2, the effect resembles that of four point sources located at the GLQ
        nodes. c) At $150\ km$ but with a higher order of 30, the effect is
        again similar to the maps in \citet{Asgharzadeh2007}.
    }
    \label{fig:sample}
\end{figure}

@@

Clearly,
there is need to determine
an optimal value of $R$
that yields the desired accuracy
in the GLQ integration.
In the following section,
we compare the computed gravitational effects
of a tesseroid model
with that of a spherical half-shell
(Fig.~\ref{fig:shell}),
for which exist analytical expressions.

@@

The gravitational potential,
gravitational attraction,
and
Marussi (gravity gradient) tensor
caused by the homogeneous spherical half-shell
shown in Fig.~\ref{fig:shell}
at a computation point
$P = (\lambda=90^\circ, \phi=0^\circ, r=r_2+h)$
are

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/spherical-shell}
    \caption{A spherical half-shell
        spanning the ranges $0^{\circ} \le \lambda \le 180^\circ$,
        $-90^\circ \le \phi \le 90^\circ$,
        and $r_1 \le r \le r_2$,
        the corresponding tesseroid model,
        the computation point $P$
        at $(\lambda=90^\circ,\phi=0^\circ,r=r_2+h)$,
        and its local coordinate system $(x, y, z)$.
    }
    \label{fig:shell}
\end{figure}

>>>>

%\documentclass[extra,mreferee]{gji}
% Use the option below to make a nicely formatted manuscript
\documentclass[extra]{gji}

\usepackage{timet}
\usepackage{graphicx}

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figs/vary-height-and-order}
    \caption{
        Example of the effect of varying
        the computation height and the Gauss-Legendre Quadrature order
        (number of nodes in each dimension).
        The $g_{xy}$ component caused by a
        $7^\circ \times 7^\circ \times 20\ km$ tesseroid
        with $2.67\ g.cm^{-3}$ density
        and top at $z=0$
        was calculated on a regular grid
        at different heights and using different orders.
        The GLQ order used was the same for all three dimensions.
        a) At $400\ km$ height and order 2, the effect is similar to that
        presented by \citet{Asgharzadeh2007}. b) At $150\ km$ height and order
        2, the effect resembles that of four point sources located at the GLQ
        nodes. c) At $150\ km$ but with a higher order of 30, the effect is
        again similar to the maps in \citet{Asgharzadeh2007}.
    }
    \label{fig:sample}
\end{figure*}

@@

Clearly,
there is need to determine
an optimal value of $R$
that yields the desired accuracy
in the GLQ integration.
In the following section,
we compare the computed gravitational effects
of a tesseroid model
with that of a spherical half-shell
for which exist analytical expressions.

@@

The gravitational potential,
gravitational attraction,
and
Marussi (gravity gradient) tensor
caused by the homogeneous spherical half-shell
at a computation point
$P = (\lambda=90^\circ, \phi=0^\circ, r=r_2+h)$
are

@@
